Literature Review

### 2018-04-24 LiteratureReview/LiteratureReview.tex
added Qualifying Report
workplan updated
updated structure on Literature Review

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin {document}

\tableofcontents

\section{Introduction to Dementia}

Identification of language impairment is important in Dementia because it aids diagnosis of specific types of dementia, which in turn can alter the prognosis and change the management of the degenerative disorder. As these differences in language are quite subtle, the varying subtypes of dementia are frequently misdiagnosed.

According to a recent report commissioned by the Alzheimer's Society, they estimate the prevalence of Dementia in the UK at approximately 815,000 people. This represents 1 in 14 of the population aged 65 or over. This report also estimates an annual healthcare spend on £4.3 billion of which approximately £85 million is spend solely on diagnosis. They also estimate that the overall impact of dementia (excluding the costs associated with early onset dementia) is £26.3 billion annually.

@@

\end {document}

>>>>

\title{Literature Review}
\date{2018-04-22}
\author{Jomar Alcantara}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin {document}
\maketitle
\newpage
\tableofcontents
\newpage

\section{Introduction to Dementia and the Literature Review}
\par
Identification of language impairment is important in Dementia because it aids diagnosis of specific types of dementia, which in turn can alter the prognosis and change the management of the degenerative disorder. As these differences in language are quite subtle, the varying subtypes of dementia are frequently misdiagnosed.
\newline
\par
According to a recent report commissioned by the Alzheimer's Society, they estimate the prevalence of Dementia in the UK at approximately 815,000 people. This represents 1 in 14 of the population aged 65 or over. This report also estimates an annual healthcare spend on £4.3 billion of which approximately £85 million is spend solely on diagnosis. They also estimate that the overall impact of dementia (excluding the costs associated with early onset dementia) is £26.3 billion annually.
\newline
\par
The purpose of this review is to seek to understand how dementia impacts speech and language production from a clinical psychology perspective. This review goes on to

% Describe how you have conducted the search. What did you search, how did you search, how did you filter.

\section{Description of Dementia}

\subsection{Alzheimer's Disease}
\subsection{Vascular Dementia}
\subsection{Dementia with Lewy Bodies}
\subsection{Parkinson's disease dementia}
\subsection{Fronto-temporal dementia}
\subsection{Mild Cognitive Impairment}

@@

\section{Conclusion}
Given the burden on the diagnosis of dementia on clinicians, it appears to be useful to find some non-invasive protocols for the early diagnosis of dementia. 
\end {document}
